---
title: "WDI_combined data"
author: "Amarachi Lauren Obioha"
date: "2024-05-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(WDI)
library(dplyr)
library(imputeTS)
library(stargazer)
library(plm)
```


```{r}
country_codes <- c(country_code_c <- c( "AUS","BRA","CAN","CHN", "FRA", "DEU", "IND", "IDN", "IRN", "ITA","JPN", "MEX", "RUS", "SAU","KOR","ESP","THA", "TUR", "GBR", "USA"))
gdp_c_1<- "NY.GDP.PCAP.KD.ZG" #GDP per capita growth annual percentage growth 
gdp_c_2 <- "NY.GDP.PCAP.CD" #GDP per capita (current US$) annual
population_c <- "SP.POP.GROW" # Population growth annual population growth rate 
government_expenditure_c <- "SE.XPD.TOTL.GB.ZS" # Government expenditure on education percentage of total government expenditure
fdi_c <- "BX.KLT.DINV.WD.GD.ZS" # 	Foreign direct investment, net inflows (% of GDP)
urbpop_c <- "SP.URB.GROW" #Urban population growth annual percentage growth
RD_c <-"GB.XPD.RSDV.GD.ZS" #Research and development expenditure (% of GDP)
```


```{r}
# control variables 
control_variables_1 <- c("NY.GDP.PCAP.KD.ZG", #GDP per capita growth annual percentage growth 
                       "SP.POP.GROW", # Population growth annual population growth rate 
                       "SE.XPD.TOTL.GB.ZS", # Government expenditure on education percentage of total government expenditure
                       "BX.KLT.DINV.WD.GD.ZS" # 	Foreign direct investment, net inflows percentage of GDP
)                     
                      
control_variables_2 <- c("NY.GDP.PCAP.CD", #GDP per capita current US$
                        "SP.URB.GROW", #Urban population growth annual percentage growth                 
                       "GB.XPD.RSDV.GD.ZS", #Research and development expenditure percentage of GDP
                       "BX.KLT.DINV.WD.GD.ZS" # 	Foreign direct investment, net inflows percentage of GDP
                       )

control_variables_3 <- c("NY.GDP.PCAP.KD.ZG", #GDP per capita growth annual percentage growth 
                       "SP.POP.GROW", # Population growth annual population growth rate 
                       "SE.XPD.TOTL.GB.ZS" # Government expenditure on education percentage of total government expenditure
                       )  

control_variables_4 <- c("NY.GDP.PCAP.CD", #GDP per capita current US$
                        "SP.URB.GROW", #Urban population growth annual percentage growth                 
                       "GB.XPD.RSDV.GD.ZS" #Research and development expenditure percentage of GDP
                       )

control_variables_5 <- c("NY.GDP.PCAP.KD.ZG", #GDP per capita growth annual percentage growth 
                       "SP.POP.GROW", # Population growth annual population growth rate 
                       "BX.KLT.DINV.WD.GD.ZS" # 	Foreign direct investment, net inflows percentage of GDP
                       ) 

control_variables_6 <- c("NY.GDP.PCAP.CD", #GDP per capita current US$
                        "SP.URB.GROW", #Urban population growth annual percentage growth                 
                       "BX.KLT.DINV.WD.GD.ZS" # 	Foreign direct investment, net inflows percentage of GDP
                       )

control_variables_7 <- c("NY.GDP.PCAP.KD.ZG", #GDP per capita growth annual percentage growth 
                       "SP.URB.GROW", #Urban population growth annual percentage growth 
                       "SE.XPD.TOTL.GB.ZS", # Government expenditure on education percentage of total government expenditure
                       "BX.KLT.DINV.WD.GD.ZS" # 	Foreign direct investment, net inflows percentage of GDP
                       )   

control_variables_8 <- c("NY.GDP.PCAP.CD", #GDP per capita (current US$)
                        "SP.POP.GROW", # Population growth annual population growth rate                 
                       "GB.XPD.RSDV.GD.ZS", #Research and development expenditure percentage of GDP
                       "BX.KLT.DINV.WD.GD.ZS" # 	Foreign direct investment, net inflows percentage of GDP
                       )
control_variables_9 <- control_variables_6 <- c("NY.GDP.PCAP.CD", #GDP per capita current US$
                        "SP.URB.GROW", #Urban population growth annual percentage growth 
                        "GB.XPD.RSDV.GD.ZS", #Research and development expenditure percentage of GDP
                       "BX.KLT.DINV.WD.GD.ZS" # 	Foreign direct investment, net inflows percentage of GDP
                       )
```



```{r}
#Data from WDI database
data_wdi_1 <- WDI(country = country_codes, indicator = control_variables_1, start = min(1990), end = max(2022), extra = TRUE)
data_wdi_2 <- WDI(country = country_codes, indicator = control_variables_2, start = min(1990), end = max(2022), extra = TRUE)
data_wdi_3 <- WDI(country = country_codes, indicator = control_variables_3, start = min(1990), end = max(2022), extra = TRUE)
data_wdi_4 <- WDI(country = country_codes, indicator = control_variables_4, start = min(1990), end = max(2022), extra = TRUE)
data_wdi_5 <- WDI(country = country_codes, indicator = control_variables_5, start = min(1990), end = max(2022), extra = TRUE)
data_wdi_6 <- WDI(country = country_codes, indicator = control_variables_6, start = min(1990), end = max(2022), extra = TRUE)
data_wdi_7 <- WDI(country = country_codes, indicator = control_variables_7, start = min(1990), end = max(2022), extra = TRUE)
data_wdi_8 <- WDI(country = country_codes, indicator = control_variables_8, start = min(1990), end = max(2022), extra = TRUE)
data_wdi_9 <- WDI(country = country_codes, indicator = control_variables_9, start = min(1990), end = max(2022), extra = TRUE)
```

#Original Data 
```{r}
library(readxl)
Original_data <- read_excel("owid-energy-data.xlsx")
View(Original_data)
```


```{r}
library(readxl)
Combined_copy <- read_excel("Combined  copy.xlsx")
View(Combined_copy)

#Extracted columns
Coal_consump_comb <- Combined_copy$coal_consumption
Natural_gas_comb <- Combined_copy$gas_consumption
Oil_consump_comb <- Combined_copy$oil_energy_per_capita
Nuclear_consump_comb<- Combined_copy$nuclear_consumption
Renewable_energy_comb <- Combined_copy$renewables_consumption

#Combining IEA database and WDI database to get major variables
length(Coal_consump_comb)
length(Natural_gas_comb)
length(Oil_consump_comb)
length(Nuclear_consump_comb)
length(Renewable_energy_comb)

Coal_consump_comb <- Coal_consump_comb[1:660]  # Adjust the length if necessary
Natural_gas_comb <- Natural_gas_comb[1:660] # Adjust the length if necessary
Oil_consump_comb <- Oil_consump_comb[1:660] # Adjust the length if necessary
Nuclear_consump_comb <- Nuclear_consump_comb[1:660] # Adjust the length if necessary
Renewable_energy_comb <- Renewable_energy_comb[1:660] # Adjust the length if necessary

#Adding variables to wdi data-1
data_wdi_1$Coal_consump_comb <- Coal_consump_comb
data_wdi_1$Natural_gas_comb <- Natural_gas_comb
data_wdi_1$Oil_consump_comb <- Oil_consump_comb
data_wdi_1$Nuclear_consump_comb <- Nuclear_consump_comb
data_wdi_1$Renewable_energy_comb <- Renewable_energy_comb

#Adding variables to wdi data-2
data_wdi_2$Coal_consump_comb <- Coal_consump_comb
data_wdi_2$Natural_gas_comb <- Natural_gas_comb
data_wdi_2$Oil_consump_comb <- Oil_consump_comb
data_wdi_2$Nuclear_consump_comb <- Nuclear_consump_comb
data_wdi_2$Renewable_energy_comb <- Renewable_energy_comb

#Adding variables to wdi data-3
data_wdi_3$Coal_consump_comb <- Coal_consump_comb
data_wdi_3$Natural_gas_comb <- Natural_gas_comb
data_wdi_3$Oil_consump_comb <- Oil_consump_comb
data_wdi_3$Nuclear_consump_comb <- Nuclear_consump_comb
data_wdi_3$Renewable_energy_comb <- Renewable_energy_comb

#Adding variables to wdi data-4
data_wdi_4$Coal_consump_comb <- Coal_consump_comb
data_wdi_4$Natural_gas_comb <- Natural_gas_comb
data_wdi_4$Oil_consump_comb <- Oil_consump_comb
data_wdi_4$Nuclear_consump_comb <- Nuclear_consump_comb
data_wdi_4$Renewable_energy_comb <- Renewable_energy_comb

#Adding variables to wdi data-5
data_wdi_5$Coal_consump_comb <- Coal_consump_comb
data_wdi_5$Natural_gas_comb <- Natural_gas_comb
data_wdi_5$Oil_consump_comb <- Oil_consump_comb
data_wdi_5$Nuclear_consump_comb <- Nuclear_consump_comb
data_wdi_5$Renewable_energy_comb <- Renewable_energy_comb

#Adding variables to wdi data-6
data_wdi_6$Coal_consump_comb <- Coal_consump_comb
data_wdi_6$Natural_gas_comb <- Natural_gas_comb
data_wdi_6$Oil_consump_comb <- Oil_consump_comb
data_wdi_6$Nuclear_consump_comb <- Nuclear_consump_comb
data_wdi_6$Renewable_energy_comb <- Renewable_energy_comb

#Adding variables to wdi data-7
data_wdi_7$Coal_consump_comb <- Coal_consump_comb
data_wdi_7$Natural_gas_comb <- Natural_gas_comb
data_wdi_7$Oil_consump_comb <- Oil_consump_comb
data_wdi_7$Nuclear_consump_comb <- Nuclear_consump_comb
data_wdi_7$Renewable_energy_comb <- Renewable_energy_comb

#Adding variables to wdi data-8
data_wdi_8$Coal_consump_comb <- Coal_consump_comb
data_wdi_8$Natural_gas_comb <- Natural_gas_comb
data_wdi_8$Oil_consump_comb <- Oil_consump_comb
data_wdi_8$Nuclear_consump_comb <- Nuclear_consump_comb
data_wdi_8$Renewable_energy_comb <- Renewable_energy_comb

#Adding variables to wdi data-9
data_wdi_9$Coal_consump_comb <- Coal_consump_comb
data_wdi_9$Natural_gas_comb <- Natural_gas_comb
data_wdi_9$Oil_consump_comb <- Oil_consump_comb
data_wdi_9$Nuclear_consump_comb <- Nuclear_consump_comb
data_wdi_9$Renewable_energy_comb <- Renewable_energy_comb
```

```{r}
#Linear interpolation
Combined_Energy_Data_1 <- data_wdi_1 %>% 
  arrange(country, year) %>%
  group_by(country) %>%
  mutate(
    Coal_consump_comb = na_interpolation(Coal_consump_comb, option = "linear"), #Linear interpolation
    Natural_gas_comb = na_interpolation(Natural_gas_comb, option = "linear"), # Linear interpolation
    Oil_consump_comb = na_interpolation(Oil_consump_comb, option = "linear"), #Linear interpolation
    Nuclear_consump_comb = na_interpolation(Nuclear_consump_comb, option = "linear"), #Linear interpolation
    Renewable_energy_comb = na_interpolation(Renewable_energy_comb, option = "linear"), #Linear interpolation
    GDP_per_Capita_1 = na_interpolation(NY.GDP.PCAP.KD.ZG, option = "linear"), # Linear interpolation
    Population_growth_1  = na_interpolation(SP.POP.GROW, option = "linear") ,     # Linear interpolation
    Govt_edu_expenditure_1 = na_interpolation (SE.XPD.TOTL.GB.ZS, option = "linear"), #Linear interpolation
    Foreign_direct_investment_1 = na_interpolation (BX.KLT.DINV.WD.GD.ZS, option = "linear") #Linear interpolation
    )

Combined_Energy_Data_2 <- data_wdi_2 %>% 
  arrange(country, year) %>%
  group_by(country) %>%
  mutate(
    Coal_consump_comb = na_interpolation(Coal_consump_comb, option = "linear"), #Linear interpolation
    Natural_gas_comb = na_interpolation(Natural_gas_comb, option = "linear"), # Linear interpolation
    Oil_consump_comb = na_interpolation(Oil_consump_comb, option = "linear"), #Linear interpolation
    Nuclear_consump_comb = na_interpolation(Nuclear_consump_comb, option = "linear"), #Linear interpolation
    Renewable_energy_comb = na_interpolation(Renewable_energy_comb, option = "linear"), #Linear interpolation
    GDP_per_Capita_2 = na_interpolation(NY.GDP.PCAP.CD, option = "linear"), # Linear interpolation
    Urban_Population_2  = na_interpolation(SP.URB.GROW, option = "linear") ,     # Linear interpolation
    Research_Dev_expenditure_2 = na_interpolation (GB.XPD.RSDV.GD.ZS, option = "linear"), #Linear interpolation
    Foreign_direct_investment_2 = na_interpolation (BX.KLT.DINV.WD.GD.ZS, option = "linear") #Linear interpolation
    )

Combined_Energy_Data_3 <- data_wdi_3 %>% 
  arrange(country, year) %>%
  group_by(country) %>%
  mutate(
    Coal_consump_comb = na_interpolation(Coal_consump_comb, option = "linear"), #Linear interpolation
    Natural_gas_comb = na_interpolation(Natural_gas_comb, option = "linear"), # Linear interpolation
    Oil_consump_comb = na_interpolation(Oil_consump_comb, option = "linear"), #Linear interpolation
    Nuclear_consump_comb = na_interpolation(Nuclear_consump_comb, option = "linear"), #Linear interpolation
    Renewable_energy_comb = na_interpolation(Renewable_energy_comb, option = "linear"), #Linear interpolation
    GDP_per_Capita_3 = na_interpolation(NY.GDP.PCAP.KD.ZG, option = "linear"), # Linear interpolation
    Population_growth_3  = na_interpolation(SP.POP.GROW, option = "linear") ,     # Linear interpolation
    Govt_edu_expenditure_3 = na_interpolation (SE.XPD.TOTL.GB.ZS, option = "linear"), #Linear interpolation
    )

Combined_Energy_Data_4 <- data_wdi_4 %>% 
  arrange(country, year) %>%
  group_by(country) %>%
  mutate(
    Coal_consump_comb = na_interpolation(Coal_consump_comb, option = "linear"), #Linear interpolation
    Natural_gas_comb = na_interpolation(Natural_gas_comb, option = "linear"), # Linear interpolation
    Oil_consump_comb = na_interpolation(Oil_consump_comb, option = "linear"), #Linear interpolation
    Nuclear_consump_comb = na_interpolation(Nuclear_consump_comb, option = "linear"), #Linear interpolation
    Renewable_energy_comb = na_interpolation(Renewable_energy_comb, option = "linear"), #Linear interpolation
    GDP_per_Capita_4 = na_interpolation(NY.GDP.PCAP.CD, option = "linear"), # Linear interpolation
    Urban_Population_4  = na_interpolation(SP.URB.GROW, option = "linear") ,     # Linear interpolation
    Research_Dev_expenditure_4 = na_interpolation (GB.XPD.RSDV.GD.ZS, option = "linear"), #Linear interpolation
    )

Combined_Energy_Data_5 <- data_wdi_5 %>% 
  arrange(country, year) %>%
  group_by(country) %>%
  mutate(
    Coal_consump_comb = na_interpolation(Coal_consump_comb, option = "linear"), #Linear interpolation
    Natural_gas_comb = na_interpolation(Natural_gas_comb, option = "linear"), # Linear interpolation
    Oil_consump_comb = na_interpolation(Oil_consump_comb, option = "linear"), #Linear interpolation
    Nuclear_consump_comb = na_interpolation(Nuclear_consump_comb, option = "linear"), #Linear interpolation
    Renewable_energy_comb = na_interpolation(Renewable_energy_comb, option = "linear"), #Linear interpolation
    GDP_per_Capita_5 = na_interpolation(NY.GDP.PCAP.KD.ZG, option = "linear"), # Linear interpolation
    Population_growth_5  = na_interpolation(SP.POP.GROW, option = "linear") ,     # Linear interpolation
    Foreign_direct_investment_5 = na_interpolation (BX.KLT.DINV.WD.GD.ZS, option = "linear") #Linear interpolation
    )

Combined_Energy_Data_6 <- data_wdi_6 %>% 
  arrange(country, year) %>%
  group_by(country) %>%
  mutate(
    Coal_consump_comb = na_interpolation(Coal_consump_comb, option = "linear"), #Linear interpolation
    Natural_gas_comb = na_interpolation(Natural_gas_comb, option = "linear"), # Linear interpolation
    Oil_consump_comb = na_interpolation(Oil_consump_comb, option = "linear"), #Linear interpolation
    Nuclear_consump_comb = na_interpolation(Nuclear_consump_comb, option = "linear"), #Linear interpolation
    Renewable_energy_comb = na_interpolation(Renewable_energy_comb, option = "linear"), #Linear interpolation
    GDP_per_Capita_6 = na_interpolation(NY.GDP.PCAP.CD, option = "linear"), # Linear interpolation
    Urban_Population_6 = na_interpolation(SP.URB.GROW, option = "linear") ,     # Linear interpolation
    Foreign_direct_investment_6 = na_interpolation (BX.KLT.DINV.WD.GD.ZS, option = "linear") #Linear interpolation
)

Combined_Energy_Data_7 <- data_wdi_7 %>% 
  arrange(country, year) %>%
  group_by(country) %>%
  mutate(
    Coal_consump_comb = na_interpolation(Coal_consump_comb, option = "linear"), #Linear interpolation
    Natural_gas_comb = na_interpolation(Natural_gas_comb, option = "linear"), # Linear interpolation
    Oil_consump_comb = na_interpolation(Oil_consump_comb, option = "linear"), #Linear interpolation
    Nuclear_consump_comb = na_interpolation(Nuclear_consump_comb, option = "linear"), #Linear interpolation
    Renewable_energy_comb = na_interpolation(Renewable_energy_comb, option = "linear"), #Linear interpolation
    GDP_per_Capita_7 = na_interpolation(NY.GDP.PCAP.KD.ZG, option = "linear"), # Linear interpolation
    Urban_growth_7 = na_interpolation(SP.URB.GROW, option = "linear") ,     # Linear interpolation
    Govt_edu_expenditure_7 = na_interpolation (SE.XPD.TOTL.GB.ZS, option = "linear"), #Linear interpolation
    Foreign_direct_investment_7 = na_interpolation (BX.KLT.DINV.WD.GD.ZS, option = "linear") #Linear interpolation
    )


Combined_Energy_Data_8 <- data_wdi_8 %>% 
  arrange(country, year) %>%
  group_by(country) %>%
  mutate(
    Coal_consump_comb = na_interpolation(Coal_consump_comb, option = "linear"), #Linear interpolation
    Natural_gas_comb = na_interpolation(Natural_gas_comb, option = "linear"), # Linear interpolation
    Oil_consump_comb = na_interpolation(Oil_consump_comb, option = "linear"), #Linear interpolation
    Nuclear_consump_comb = na_interpolation(Nuclear_consump_comb, option = "linear"), #Linear interpolation
    Renewable_energy_comb = na_interpolation(Renewable_energy_comb, option = "linear"), #Linear interpolation
    GDP_per_Capita_8 = na_interpolation(NY.GDP.PCAP.CD, option = "linear"), # Linear interpolation
    Population_growth_8  = na_interpolation(SP.POP.GROW, option = "linear") ,     # Linear interpolation
    Research_Dev_expenditure_8 = na_interpolation (GB.XPD.RSDV.GD.ZS, option = "linear"), #Linear interpolation
    Foreign_direct_investment_8 = na_interpolation (BX.KLT.DINV.WD.GD.ZS, option = "linear") #Linear interpolation
    )

Combined_Energy_Data_9 <- data_wdi_9 %>% 
  arrange(country, year) %>%
  group_by(country) %>%
  mutate(
    Coal_consump_comb = na_interpolation(Coal_consump_comb, option = "linear"), #Linear interpolation
    Natural_gas_comb = na_interpolation(Natural_gas_comb, option = "linear"), # Linear interpolation
    Oil_consump_comb = na_interpolation(Oil_consump_comb, option = "linear"), #Linear interpolation
    Nuclear_consump_comb = na_interpolation(Nuclear_consump_comb, option = "linear"), #Linear interpolation
    Renewable_energy_comb = na_interpolation(Renewable_energy_comb, option = "linear"), #Linear interpolation
    GDP_per_Capita_9 = na_interpolation(NY.GDP.PCAP.CD, option = "linear"), # Linear interpolation
    Urban_Population_9 = na_interpolation(SP.URB.GROW, option = "linear") ,     # Linear interpolation
    Research_Dev_expenditure_9 = na_interpolation (GB.XPD.RSDV.GD.ZS, option = "linear"), #Linear interpolation
    Foreign_direct_investment_9 = na_interpolation (BX.KLT.DINV.WD.GD.ZS, option = "linear") #Linear interpolation
)

```


```{r}
#Removing unnecessary columns
Energy_Data_1 <- Combined_Energy_Data_1 %>% dplyr::select(-NY.GDP.PCAP.KD.ZG, -SP.POP.GROW, -SE.XPD.TOTL.GB.ZS, -BX.KLT.DINV.WD.GD.ZS)
Energy_Data_2 <- Combined_Energy_Data_2 %>% dplyr::select(-NY.GDP.PCAP.CD, -SP.URB.GROW,            -GB.XPD.RSDV.GD.ZS, -BX.KLT.DINV.WD.GD.ZS)
Energy_Data_3 <- Combined_Energy_Data_3 %>% dplyr::select (-NY.GDP.PCAP.KD.ZG, -SP.POP.GROW, -SE.XPD.TOTL.GB.ZS)  
Energy_Data_4 <- Combined_Energy_Data_4 %>% dplyr::select (-NY.GDP.PCAP.CD, -SP.URB.GROW,                 
-GB.XPD.RSDV.GD.ZS)
Energy_Data_5 <- Combined_Energy_Data_5 %>% dplyr::select (-NY.GDP.PCAP.KD.ZG, -SP.POP.GROW, -BX.KLT.DINV.WD.GD.ZS) 
Energy_Data_6 <- Combined_Energy_Data_6 %>% dplyr::select (-NY.GDP.PCAP.CD, -SP.URB.GROW,-GB.XPD.RSDV.GD.ZS,  -BX.KLT.DINV.WD.GD.ZS)
Energy_Data_7 <- Combined_Energy_Data_7 %>% dplyr::select (-NY.GDP.PCAP.KD.ZG,-SP.URB.GROW,
-SE.XPD.TOTL.GB.ZS,-BX.KLT.DINV.WD.GD.ZS) 
Energy_Data_8 <- Combined_Energy_Data_8 %>% dplyr::select (-NY.GDP.PCAP.CD,-SP.POP.GROW,                 -GB.XPD.RSDV.GD.ZS,-BX.KLT.DINV.WD.GD.ZS)
Energy_Data_9 <- Combined_Energy_Data_9 %>% dplyr::select (-NY.GDP.PCAP.CD, -SP.URB.GROW, -GB.XPD.RSDV.GD.ZS, -BX.KLT.DINV.WD.GD.ZS)
```


```{r}
#Using Stargazer- Descriptive Statistics
stargazer(Energy_Data_1, type = "text")
stargazer(Energy_Data_2, type = "text")
stargazer(Energy_Data_3, type = "text")
stargazer(Energy_Data_4, type = "text")
stargazer(Energy_Data_5, type = "text")
stargazer(Energy_Data_6, type = "text")
stargazer(Energy_Data_7, type = "text")
stargazer(Energy_Data_8, type = "text")
stargazer(Energy_Data_9, type = "text")
```


```{r}
#Descriptive Statistics using summary
summary(Energy_Data_1)
summary(Energy_Data_2)
summary(Energy_Data_3)
summary(Energy_Data_4)
summary(Energy_Data_5)
summary(Energy_Data_6)
summary(Energy_Data_7)
summary(Energy_Data_8)
summary(Energy_Data_9)
```

#Choice between Random and Fixed effects
```{r}
#Fixed effect
Model_fix <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb, data = Combined_copy, index = c("country", "year"),
                   model = "within")  # or "within" for fixed effects model) 

Model_fix6 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + GDP_per_Capita_6 + Urban_Population_6 + Foreign_direct_investment_6, data = Energy_Data_6, , index = c("country", "year"),
                   model = "within")  # or "within" for fixed effects model)

stargazer( Model_fix, Model_fix6, type = "text")
```


```{r}
#Using Hausman test 
# Perform the Hausman test
hausman_test <- phtest(Model, Model_fix)
# Print the Hausman test results
print(hausman_test)
print(hausman_test6)
```
#Results
HO:The preferred model is random effects 
H1:The preferred model is fixed effects
We reject the null hypothesis and conclude that the preferred model is the fixed effects.


#Ordinary Least Squares Method (OLS)
```{r}
#Panel Linear Regression for 20 countries 
# Create a multiple regression model with control variables
library(stargazer)
Model <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb, data = Combined_copy, index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model) 
Model1 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + GDP_per_Capita_1 + Population_growth_1 + Govt_edu_expenditure_1 + Foreign_direct_investment_1, data = Energy_Data_1, index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)
Model2 <- plm (Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + GDP_per_Capita_2 + Urban_Population_2 + Research_Dev_expenditure_2 +  Foreign_direct_investment_2, data = Energy_Data_2, , index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)
Model3 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + GDP_per_Capita_3 + Population_growth_3 + Govt_edu_expenditure_3, data = Energy_Data_3, 
              , index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)
Model4 <- plm (Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + GDP_per_Capita_4 + Urban_Population_4 + Research_Dev_expenditure_4, data = Energy_Data_4, , index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)
Model5 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + GDP_per_Capita_5 + Population_growth_5 + Foreign_direct_investment_5, data = Energy_Data_5, , index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)

Model6 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + GDP_per_Capita_6 + Urban_Population_6 + Foreign_direct_investment_6, data = Energy_Data_6, , index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)
Model7 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + GDP_per_Capita_7 + Urban_growth_7 + Govt_edu_expenditure_7 + Foreign_direct_investment_7, data = Energy_Data_7, , index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)
Model8 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + GDP_per_Capita_8 + Population_growth_8 + Research_Dev_expenditure_8 +  Foreign_direct_investment_8, data = Energy_Data_8, , index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)
Model9 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + GDP_per_Capita_9 + Urban_Population_9 + Research_Dev_expenditure_9 + Foreign_direct_investment_9, data = Energy_Data_9, , index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)
stargazer(Model, Model1, Model2, Model3, Model4, type = "text")
```


```{r}
stargazer(Model5, Model6, Model7, Model8, Model9, type = "text")
```

#Note
In Model6, all dependent variables are significant. 

```{r}
#Using Variance Inflation Factor (VIF) test to check for multicollinearity
library(car)
vif <- vif(Model)
print(vif)
```

```{r}
library(car)
vif_1 <- vif(Model1)
print(vif_1)
```

```{r}
library(car)
vif_2 <- vif(Model2)
print(vif_2)
```

```{r}
library(car)
vif_3 <- vif(Model3)
print(vif_3)
```

```{r}
library(car)
vif_4 <- vif(Model4)
print(vif_4)
```

```{r}
library(car)
vif_5 <- vif(Model5)
print(vif_5)
```

```{r}
library(car)
vif_6 <- vif(Model6)
print(vif_6)
```

```{r}
library(car)
vif_7 <- vif(Model7)
print(vif_7)
```

```{r}
library(car)
vif_8 <- vif(Model8)
print(vif_8)
```

```{r}
library(car)
vif_9 <- vif(Model9)
print(vif_9)
```
#Results
Interpretation Multicollinearity occurs when more than two explanatory variables are strongly correlated linearly (Belsley,1991).The VIF calculates how much multicollinearity has affected the calculated regression coefficients’ variance (Krishna, 1975). Using the Variance Inflation Factor (VIF) to check for multicollinearity, VIF values higher than 5 indicates multicollinearity (Heiss, 2016)

```{r}
#Using the Breusch-Pagan Test to test for heteroscedasticity.
library(lmtest)
(BP <- bptest(Model))
```

```{r}
(BP1 <- bptest(Model1))
```

```{r}
(BP2 <- bptest(Model2))
```

```{r}
(BP3 <- bptest(Model3))
```

```{r}
(BP4 <- bptest(Model4))
```

```{r}
(BP5 <- bptest(Model5))
```


```{r}
(BP6 <- bptest(Model6))
```

```{r}
(BP7 <- bptest(Model7))
```

```{r}
(BP8 <- bptest(Model8))
```

```{r}
(BP9 <- bptest(Model9))
```
#Results
Same results < 2.2e-16 which is less than the 0.05 significance level. 

H0:There is no heteroscedasticity i.e there is homoscedasticity
H1:There is heteroscedasticity 

We reject the null hypothesis and conclude that there is a presence of heteroscedasticity. 


```{r}
#Use a joint hypothesis test to detect whether all coefficients are zero
library(AER)
HNull <- c("Coal_consump_comb=0", "Oil_consump_comb=0", "Nuclear_consump_comb=0", "Natural_gas_comb=0")
HNull1 <- c("Coal_consump_comb=0", "Oil_consump_comb=0", "Nuclear_consump_comb=0", "Natural_gas_comb=0","GDP_per_Capita_1=0","Population_growth_1=0","Govt_edu_expenditure_1=0","Foreign_direct_investment_1=0")
HNull2 <- c("Coal_consump_comb=0", "Oil_consump_comb=0", "Nuclear_consump_comb=0", "Natural_gas_comb=0", "GDP_per_Capita_2","Urban_Population_2", "Research_Dev_expenditure_2","Foreign_direct_investment_2")
HNull3 <- c("Coal_consump_comb=0", "Oil_consump_comb=0", "Nuclear_consump_comb=0", "Natural_gas_comb=0", "GDP_per_Capita_3", "Population_growth_3","Govt_edu_expenditure_3")
HNull4 <- c("Coal_consump_comb=0", "Oil_consump_comb=0", "Nuclear_consump_comb=0", "Natural_gas_comb=0","GDP_per_Capita_4","Urban_Population_4","Research_Dev_expenditure_4")
HNull5 <- c("Coal_consump_comb=0", "Oil_consump_comb=0", "Nuclear_consump_comb=0", "Natural_gas_comb=0","GDP_per_Capita_5", "Population_growth_5", "Foreign_direct_investment_5")
HNull6 <- c("Coal_consump_comb=0", "Oil_consump_comb=0", "Nuclear_consump_comb=0", "Natural_gas_comb=0","GDP_per_Capita_6", "Urban_Population_6","Foreign_direct_investment_6")
HNull7 <- c("Coal_consump_comb=0", "Oil_consump_comb=0", "Nuclear_consump_comb=0", "Natural_gas_comb=0", "GDP_per_Capita_7", "Urban_growth_7", "Govt_edu_expenditure_7", "Foreign_direct_investment_7")
HNull8 <- c("Coal_consump_comb=0", "Oil_consump_comb=0", "Nuclear_consump_comb=0", "Natural_gas_comb=0","GDP_per_Capita_8","Population_growth_8","Research_Dev_expenditure_8","Foreign_direct_investment_8")
HNull9 <- c("Coal_consump_comb=0", "Oil_consump_comb=0", "Nuclear_consump_comb=0", "Natural_gas_comb=0", "GDP_per_Capita_9", "Urban_Population_9", "Research_Dev_expenditure_9", "Foreign_direct_investment_9" )
linearHypothesis(Model, HNull)
linearHypothesis(Model1, HNull1)
linearHypothesis(Model2, HNull2)
linearHypothesis(Model3, HNull3)
linearHypothesis(Model4, HNull4)
linearHypothesis(Model5, HNull5)
linearHypothesis(Model6, HNull6)
linearHypothesis(Model7, HNull7)
linearHypothesis(Model8, HNull8)
linearHypothesis(Model9, HNull9)
```

#Results 
For the interpretation of the result above, the null and alternative hypothesis are formulated below: 
H0: All coefficients in the Model are zero 
H1: At least one coefficient in the Model  is not equal to zero
If the H0 is true, it shows that is no evidence of a significant relationship between the dependent variable and the independent variables. If the H1 is true, it shows that there is an evidence of a significant relationship between the dependent variable and the independent variables.
From the results above, the calculated p-value is 2.2e-16 which is less than the significance level of 0.05, therefore we reject the null hypothesis that all coefficients in the Model1 are equal to zero and conclude that at least one coefficient in Model1 is not equal to zero and there is evidence of significant relationship between the dependent and independent variables.


```{r}
#Using the Jarque-Bera-Test to test for normality of the residuals
library(tseries)
(jbt <- jarque.bera.test(Model$residuals))
(jbt1 <- jarque.bera.test(Model1$residuals))
(jbt2 <- jarque.bera.test(Model2$residuals))
(jbt3 <- jarque.bera.test(Model3$residuals))
(jbt4 <- jarque.bera.test(Model4$residuals))
(jbt5 <- jarque.bera.test(Model5$residuals))
(jbt6 <- jarque.bera.test(Model6$residuals))
(jbt7 <- jarque.bera.test(Model7$residuals))
(jbt8 <- jarque.bera.test(Model8$residuals))
(jbt9 <- jarque.bera.test(Model9$residuals))
```

#Results
The Jarque-Bera-Test is a test that determines if a given data have the skewness and kurtosis that a consistent with a normal distribution (Jarque & Bera, 1980).

H0: residuals are not normally distributed.                                                                   H1: residuals are normally distributed.

From the result above, the p-value is 2.2e-16 which is less than the 0.05 significance interval so we reject the H0 and can conclude that our residuals indeed are normally distributed


```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model)
t_test <- t.test(residuals)
print(t_test)
```


```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model1)
t_test1 <- t.test(residuals)
print(t_test1)
```


```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model2)
t_test2 <- t.test(residuals)
print(t_test2)
```


```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model3)
t_test3 <- t.test(residuals)
print(t_test3)
```


```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model4)
t_test4 <- t.test(residuals)
print(t_test4)
```


```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model5)
t_test5 <- t.test(residuals)
print(t_test5)
```


```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model6)
t_test6 <- t.test(residuals)
print(t_test6)
```


```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model7)
t_test7 <- t.test(residuals)
print(t_test7)
```


```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model8)
t_test8 <- t.test(residuals)
print(t_test8)
```


```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model9)
t_test9 <- t.test(residuals)
print(t_test9)
```
#Results
H0: The mean of the residuals is equal to zero, indicating that the zero mean assumption holds.
H1: The mean of the residuals is not equal to zero, indicating that the zero mean assumption does not hold.
Since the p-value is greater than 0.05, we fail to reject the null hypothesis and can conclude that the mean of the residuals is equal to zero.


#Using Polynomials
```{r}
Model_poly <- plm(Renewable_energy_comb ~ poly(Coal_consump_comb) + poly(Natural_gas_comb) + poly(Oil_consump_comb) + poly(Nuclear_consump_comb), data = Combined_copy, index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model) 
Model_poly1 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + poly(GDP_per_Capita_1) +poly(Population_growth_1) + poly(Govt_edu_expenditure_1) + poly(Foreign_direct_investment_1), data = Energy_Data_1, index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)
Model_poly2 <- plm (Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + poly(GDP_per_Capita_2) + poly(Urban_Population_2) + poly(Research_Dev_expenditure_2) + poly(Foreign_direct_investment_2), data = Energy_Data_2, , index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)
Model_poly3 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + poly(GDP_per_Capita_3) + poly(Population_growth_3) + poly(Govt_edu_expenditure_3), data = Energy_Data_3, index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)
Model_poly4 <- plm (Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + poly(GDP_per_Capita_4) + poly(Urban_Population_4) + poly(Research_Dev_expenditure_4), data = Energy_Data_4, , index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)
Model_poly5 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + poly(GDP_per_Capita_5) + poly(Population_growth_5) + poly(Foreign_direct_investment_5), data = Energy_Data_5, , index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)
Model_poly6 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + poly(GDP_per_Capita_6) + poly(Urban_Population_6) + poly(Foreign_direct_investment_6), data = Energy_Data_6, , index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)
Model_poly7 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + poly(GDP_per_Capita_7) + poly(Urban_growth_7) + poly(Govt_edu_expenditure_7) + poly(Foreign_direct_investment_7), data = Energy_Data_7, , index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)
Model_poly8 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + poly(GDP_per_Capita_8) + poly(Population_growth_8) + poly(Research_Dev_expenditure_8) + poly(Foreign_direct_investment_8), data = Energy_Data_8, , index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)
Model_poly9 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + poly(GDP_per_Capita_9) + poly(Urban_Population_9) + poly(Research_Dev_expenditure_9) + poly(Foreign_direct_investment_9), data = Energy_Data_9, , index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)
stargazer(Model_poly, Model_poly1, Model_poly2, Model_poly3, Model_poly4, type = "text")
```


```{r}
stargazer(Model_poly5, Model_poly6, Model_poly7, Model_poly8, Model_poly9, type = "text")
```

#Note
In Modelpoly6, all dependent variables are siginificant

```{r}
(BP_poly <- bptest(Model_poly))
```

```{r}
(BP_poly1 <- bptest(Model_poly1))
```

```{r}
(BP_poly2 <- bptest(Model_poly2))
```


```{r}
(BP_poly3 <- bptest(Model_poly3))
```


```{r}
(BP_poly4 <- bptest(Model_poly4))
```


```{r}
(BP_poly5 <- bptest(Model_poly5))
```


```{r}
(BP_poly6 <- bptest(Model_poly6))
```


```{r}
(BP_poly7 <- bptest(Model_poly7))
```

```{r}
(BP_poly8 <- bptest(Model_poly8))
```

```{r}
(BP_poly9 <- bptest(Model_poly9))
```
#Results
Same results < 2.2e-16 which is less than the 0.05 significance level. 

H0:There is no heteroscedasticity i.e there is homoscedasticity
H1:There is heteroscedasticity 

We reject the null hypothesis and conclude that there is a presence of heteroscedasticity. 


```{r}
library(car)
vif_poly <- vif(Model_poly)
print(vif_poly)
```


```{r}
library(car)
vif_poly_1 <- vif(Model_poly1)
print(vif_poly_1)
```

```{r}
library(car)
vif_poly_2 <- vif(Model_poly2)
print(vif_poly_2)
```

```{r}
library(car)
vif_poly_3 <- vif(Model_poly3)
print(vif_poly_3)
```

```{r}
library(car)
vif_poly_4 <- vif(Model_poly4)
print(vif_poly_4)
```

```{r}
library(car)
vif_poly_5 <- vif(Model_poly5)
print(vif_poly_5)
```

```{r}
library(car)
vif_poly_6 <- vif(Model_poly6)
print(vif_poly_6)
```

```{r}
library(car)
vif_poly_7 <- vif(Model_poly7)
print(vif_poly_7)
```

```{r}
library(car)
vif_poly_8 <- vif(Model_poly8)
print(vif_poly_8)
```

```{r}
library(car)
vif_poly_9 <- vif(Model_poly9)
print(vif_poly_9)
```
#Results
Interpretation Multicollinearity occurs when more than two explanatory variables are strongly correlated linearly (Belsley,1991).The VIF calculates how much multicollinearity has affected the calculated regression coefficients’ variance (Krishna, 1975). Using the Variance Inflation Factor (VIF) to check for multicollinearity, VIF values higher than 5 indicates multicollinearity (Heiss, 2016)


```{r}
#Use a joint hypothesis test to detect whether all coefficients are zero
library(AER)
HNull_poly <- c("poly(Coal_consump_comb)=0", "poly(Oil_consump_comb)=0", "poly(Nuclear_consump_comb)=0", "poly(Natural_gas_comb)=0")
HNull_poly1 <- c("Coal_consump_comb=0", "Oil_consump_comb=0", "Nuclear_consump_comb=0", "Natural_gas_comb=0","poly(GDP_per_Capita_1)=0","poly(Population_growth_1)=0","poly(Govt_edu_expenditure_1)=0","poly(Foreign_direct_investment_1)=0")
HNull_poly2 <- c("Coal_consump_comb=0", "Oil_consump_comb=0", "Nuclear_consump_comb=0", "Natural_gas_comb=0", "poly(GDP_per_Capita_2)=0","poly(Urban_Population_2)=0","poly(Research_Dev_expenditure_2)=0","poly(Foreign_direct_investment_2)=0")
HNull_poly3 <- c("Coal_consump_comb=0", "Oil_consump_comb=0", "Nuclear_consump_comb=0", "Natural_gas_comb=0", "poly(GDP_per_Capita_3)=0", "poly(Population_growth_3)=0","poly(Govt_edu_expenditure_3)=0")
HNull_poly4 <- c("Coal_consump_comb=0", "Oil_consump_comb=0", "Nuclear_consump_comb=0", "Natural_gas_comb=0","poly(GDP_per_Capita_4)=0","poly(Urban_Population_4)=0","poly(Research_Dev_expenditure_4)=0")
HNull_poly5 <- c("Coal_consump_comb=0", "Oil_consump_comb=0", "Nuclear_consump_comb=0", "Natural_gas_comb=0","poly(GDP_per_Capita_5)=0", "poly(Population_growth_5)=0", "poly(Foreign_direct_investment_5)=0")
HNull_poly6 <- c("Coal_consump_comb=0", "Oil_consump_comb=0", "Nuclear_consump_comb=0", "Natural_gas_comb=0","poly(GDP_per_Capita_6)=0", "poly(Urban_Population_6)=0","poly(Foreign_direct_investment_6)=0")
HNull_poly7 <- c("Coal_consump_comb=0", "Oil_consump_comb=0", "Nuclear_consump_comb=0", "Natural_gas_comb=0", "poly(GDP_per_Capita_7)=0", "poly(Urban_growth_7)=0", "poly(Govt_edu_expenditure_7)=0", "poly(Foreign_direct_investment_7)=0")
HNull_poly8 <- c("Coal_consump_comb=0", "Oil_consump_comb=0", "Nuclear_consump_comb=0", "Natural_gas_comb=0","poly(GDP_per_Capita_8)=0","poly(Population_growth_8)=0","poly(Research_Dev_expenditure_8)=0","poly(Foreign_direct_investment_8)=0")
HNull_poly9 <- c("Coal_consump_comb=0", "Oil_consump_comb=0", "Nuclear_consump_comb=0", "Natural_gas_comb=0", "poly(GDP_per_Capita_9)=0", "poly(Urban_Population_9)=0", "poly(Research_Dev_expenditure_9)=0", "poly(Foreign_direct_investment_9)=0" )
linearHypothesis(Model_poly,  HNull_poly)
linearHypothesis(Model_poly1, HNull_poly1)
linearHypothesis(Model_poly2, HNull_poly2)
linearHypothesis(Model_poly3, HNull_poly3)
linearHypothesis(Model_poly4, HNull_poly4)
linearHypothesis(Model_poly5, HNull_poly5)
linearHypothesis(Model_poly6, HNull_poly6)
linearHypothesis(Model_poly7, HNull_poly7)
linearHypothesis(Model_poly8, HNull_poly8)
linearHypothesis(Model_poly9, HNull_poly9)
```

#Results 
For the interpretation of the result above, the null and alternative hypothesis are formulated below: 
H0: All coefficients in the Model are zero 
H1: At least one coefficient in the Model  is not equal to zero
If the H0 is true, it shows that is no evidence of a significant relationship between the dependent variable and the independent variables. If the H1 is true, it shows that there is an evidence of a significant relationship between the dependent variable and the independent variables.
From the results above, the calculated p-value is 2.2e-16 which is less than the significance level of 0.05, therefore we reject the null hypothesis that all coefficients in the Model1 are equal to zero and conclude that at least one coefficient in Model1 is not equal to zero and there is evidence of significant relationship between the dependent and independent variables.


```{r}
#Using the Jarque-Bera-Test to test for normality of the residuals
library(tseries)
(jbt_poly <- jarque.bera.test(Model_poly$residuals))
(jbt_poly1 <- jarque.bera.test(Model_poly1$residuals))
(jbt_poly2 <- jarque.bera.test(Model_poly2$residuals))
(jbt_poly3 <- jarque.bera.test(Model_poly3$residuals))
(jbt_poly4 <- jarque.bera.test(Model_poly4$residuals))
(jbt_poly5 <- jarque.bera.test(Model_poly5$residuals))
(jbt_poly6 <- jarque.bera.test(Model_poly6$residuals))
(jbt_poly7 <- jarque.bera.test(Model_poly7$residuals))
(jbt_poly8 <- jarque.bera.test(Model_poly8$residuals))
(jbt_poly9 <- jarque.bera.test(Model_poly9$residuals))
```

#Results
The Jarque-Bera-Test is a test that determines if a given data have the skewness and kurtosis that a consistent with a normal distribution (Jarque & Bera, 1980).

H0: residuals are not normally distributed.                                                                   H1: residuals are normally distributed.

From the result above, the p-value is 2.2e-16 which is less than the 0.05 significance interval so we reject the H0 and can conclude that our residuals indeed are normally distributed



```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model_poly)
t_test_poly <- t.test(residuals)
print(t_test_poly)
```


```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model_poly1)
t_test_poly1 <- t.test(residuals)
print(t_test_poly1)
```


```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model_poly2)
t_test_poly2 <- t.test(residuals)
print(t_test_poly2)
```


```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model_poly3)
t_test_poly3 <- t.test(residuals)
print(t_test_poly3)
```


```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model_poly4)
t_test_poly4 <- t.test(residuals)
print(t_test_poly4)
```

```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model_poly5)
t_test_poly5 <- t.test(residuals)
print(t_test_poly5)
```

```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model_poly6)
t_test_poly6 <- t.test(residuals)
print(t_test_poly6)
```

```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model_poly7)
t_test_poly7 <- t.test(residuals)
print(t_test_poly7)
```

```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model_poly8)
t_test_poly8 <- t.test(residuals)
print(t_test_poly8)
```


```{r}
#Test for Zero Mean OLS assumption. 
residuals <- residuals(Model_poly9)
t_test_poly9 <- t.test(residuals)
print(t_test_poly9)
```
#Results
H0: The mean of the residuals is equal to zero, indicating that the zero mean assumption holds.
H1: The mean of the residuals is not equal to zero, indicating that the zero mean assumption does not hold.
Since the p-value is greater than 0.05, we fail to reject the null hypothesis and can conclude that the mean of the residuals is equal to zero.


```{r}
#Addressing heteroscedasticity using Heteroskedasticity-Robust (HC) standard errors
# Obtain robust standard errors
robust <- coeftest(Model1, vcov = vcovHC(Model))
print(robust)
```

```{r}
summary(Model)
```


```{r}
#Addressing heteroscedasticity using Heteroskedasticity-Robust (HC) standard errors
# Obtain robust standard errors
robust1 <- coeftest(Model1, vcov = vcovHC(Model1))
print(robust1)
```

```{r}
summary(Model1)
```

#Results of Heteroskedasticity-Robust (HC) standard errors
Larger standard errors in the HC-robust summary indicate that the HC-robust standard errors provide a more accurate reflection of the true variability, particularly when heteroskedasticity is present.In summary, the standard errors from the HC-robust standard errors provide information about the precision of the coefficient estimates in the presence of heteroskedasticity.

```{r}
#Addressing heteroscedasticity using Heteroskedasticity-Robust (HC) standard errors
# Obtain robust standard errors
robust2 <- coeftest(Model2, vcov = vcovHC(Model2))
print(robust2)
```

```{r}
summary(Model2)
```


```{r}
#Addressing heteroscedasticity using Heteroskedasticity-Robust (HC) standard errors
# Obtain robust standard errors
robust6 <- coeftest(Model6, vcov = vcovHC(Model6))
print(robust6)
```


```{r}
summary(Model6)
```


#Explanation of Heteroskedasticity and Utilization of HC Standard Errors
In the regression analysis, we aimed to examine the relationship between various independent variables and the dependent variable. However, during the analysis, I encountered a common statistical issue known as heteroskedasticity. Heteroskedasticity occurs when the variability of the errors in a regression model is not constant across observations. This violation of the assumption of homoscedasticity can lead to biased standard errors and unreliable inference about the significance of the coefficients.

To address this issue, I employed Heteroskedasticity-Robust (HC) standard errors. These standard errors provide more accurate estimates when heteroskedasticity is present, as they adjust for the non-constant variance of the errors. By using HC standard errors,the aim is to ensure the validity and reliability of the regression analysis, despite the presence of heteroskedasticity.

#Interpretation of Results

Upon applying HC standard errors to our regression model, I observed several noteworthy findings:

For coefficients such as Coal_consump_comb, Natural_gas_comb, and Oil_consump_comb, we found statistically significant estimates with p-values indicating high significance. The HC standard errors associated with these coefficients were larger compared to the standard errors obtained from traditional methods. This indicates higher uncertainty in the coefficient estimates due to the presence of heteroskedasticity. Despite this increased uncertainty, the coefficients remained statistically significant, suggesting robust relationships between these variables and the dependent variable.

Conversely, coefficients such as Nuclear_consump_comb, GDP_per_Capita_1, Population_growth_1, Govt_edu_expenditure_1, and Foreign_direct_investment_1 showed no statistical significance. While the HC standard errors for these coefficients were also larger, indicating increased uncertainty, their lack of significance suggests that these variables may not have a significant effect on the dependent variable in our model.

By accounting for the non-constant variance of the errors, I obtained more accurate estimates of the standard errors and made reliable inferences about the significance of the coefficient estimates. Despite the increased uncertainty associated with HC standard errors, our analysis provided valuable insights into the relationships between the independent and dependent variables in our research model.

#Using polynimials
```{r}
#Addressing heteroscedasticity using Heteroskedasticity-Robust (HC) standard errors
# Obtain robust standard errors
robust_poly <- coeftest(Model_poly, vcov = vcovHC(Model_poly))
print(robust_poly)
```

```{r}
summary(Model_poly)
```

```{r}
#Addressing heteroscedasticity using Heteroskedasticity-Robust (HC) standard errors
# Obtain robust standard errors
robust_poly6 <- coeftest(Model_poly6, vcov = vcovHC(Model_poly6))
print(robust_poly6)
```

```{r}
summary(Model_poly6)
```


#Using log-log methods
```{r}
Model_log <- plm(log(Renewable_energy_comb) ~ log(Coal_consump_comb) + log(Natural_gas_comb) + log(Oil_consump_comb) + log(Nuclear_consump_comb), data = Combined_copy, index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model
```
#My data is not compatible using log-log method as I consecutively get this error below: Error in model.matrix.pdata.frame(data) : model matrix or response contains non-finite values (NA/NaN/Inf/-Inf)

```{r}
Model_log6 <- plm(log(Renewable_energy_comb) ~ log(Coal_consump_comb) + log(Natural_gas_comb) + log(Oil_consump_comb) + log(Nuclear_consump_comb) + log(GDP_per_Capita_6) + log(Urban_Population_6) + log(Foreign_direct_investment_6), data = Energy_Data_6, , index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)
```

#My data is not compatible using log-log method as I consecutively get this error : Error in model.matrix.pdata.frame(data) : model matrix or response contains non-finite values (NA/NaN/Inf/-Inf)

#Using linear-log method
```{r}
Model_linear_log <- plm((Renewable_energy_comb) ~ log(Coal_consump_comb) + log(Natural_gas_comb) + log(Oil_consump_comb) + log(Nuclear_consump_comb), data = Combined_copy, index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model
```

#My data is not compatible using log-log method as I consecutively get this error : Error in model.matrix.pdata.frame(data) : model matrix or response contains non-finite values (NA/NaN/Inf/-Inf)

```{r}
Model_linear_log6 <- plm(Renewable_energy_comb ~ log(Coal_consump_comb) + log(Natural_gas_comb) + log(Oil_consump_comb) + log(Nuclear_consump_comb) + log(GDP_per_Capita_6) + log(Urban_Population_6) + log(Foreign_direct_investment_6), data = Energy_Data_6, , index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)
```

#My data is not compatible using log-log method as I consecutively get this error : Error in model.matrix.pdata.frame(data) : model matrix or response contains non-finite values (NA/NaN/Inf/-Inf)

```{r}
#Using Ramsey’s Regression Equation Specification Error (RESET)
# Run RESET test (joint F-test on squared predicted values)
predicted1 <- fitted(Model1)
predicted_squared1 <- predicted^2
Model_reset1<- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + GDP_per_Capita_1 + Population_growth_1 + Govt_edu_expenditure_1 + Foreign_direct_investment_1 + I(predicted_squared1), data = Energy_Data_1, index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)

predicted2 <- fitted(Model2)
predicted_squared2 <- predicted^2
Model_reset2 <- plm (Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + GDP_per_Capita_2 + Urban_Population_2 + Research_Dev_expenditure_2 +  Foreign_direct_investment_2 +  I(predicted_squared2), data = Energy_Data_2, , index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)

predicted3 <- fitted(Model3)
predicted_squared3 <- predicted^2
Model_reset3 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + GDP_per_Capita_3 + Population_growth_3 + Govt_edu_expenditure_3+ I(predicted_squared3), data = Energy_Data_3,  index = c("country", "year"), model = "random")  # or "within" for fixed effects model)

predicted4 <- fitted(Model4)
predicted_squared4 <- predicted^2
Model_reset4 <- plm (Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + GDP_per_Capita_4 + Urban_Population_4 + Research_Dev_expenditure_4 +   I(predicted_squared4), data = Energy_Data_4, index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)

predicted5 <- fitted(Model5)
predicted_squared5 <- predicted^2
Model_reset5 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + GDP_per_Capita_5 + Population_growth_5 + Foreign_direct_investment_5  + I(predicted_squared5), data = Energy_Data_5,  index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)

predicted6 <- fitted(Model6)
predicted_squared6 <- predicted^2
Model_reset6 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + GDP_per_Capita_6 + Urban_Population_6 + Foreign_direct_investment_6 + I(predicted_squared6), data = Energy_Data_6, index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)

predicted7 <- fitted(Model7)
predicted_squared7 <- predicted^2
Model_reset7 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + GDP_per_Capita_7 + Urban_growth_7 + Govt_edu_expenditure_7 + Foreign_direct_investment_7 + I(predicted_squared7), data = Energy_Data_7, index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)

predicted8 <- fitted(Model8)
predicted_squared8 <- predicted^2
Model_reset8 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + GDP_per_Capita_8 + Population_growth_8 + Research_Dev_expenditure_8 +  Foreign_direct_investment_8 + I(predicted_squared8), data = Energy_Data_8, index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)

predicted9 <- fitted(Model9)
predicted_squared9 <- predicted^2
Model_reset9 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + GDP_per_Capita_9 + Urban_Population_9 + Research_Dev_expenditure_9 + Foreign_direct_investment_9+ I(predicted_squared8), data = Energy_Data_9,  index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)

# Extract RESET test result
reset_test_result1<- summary(Model_reset1)$fstatistic
reset_test_result2<- summary(Model_reset2)$fstatistic
reset_test_result3<- summary(Model_reset3)$fstatistic
reset_test_result4<- summary(Model_reset4)$fstatistic
reset_test_result5<- summary(Model_reset5)$fstatistic
reset_test_result6<- summary(Model_reset6)$fstatistic
reset_test_result7<- summary(Model_reset7)$fstatistic
reset_test_result8<- summary(Model_reset8)$fstatistic
reset_test_result9<- summary(Model_reset9)$fstatistic

# Print RESET test results
print(reset_test_result1)
print(reset_test_result2)
print(reset_test_result3)
print(reset_test_result4)
print(reset_test_result5)
print(reset_test_result6)
print(reset_test_result7)
print(reset_test_result8)
print(reset_test_result9)
```


```{r}
#Using Ramsey’s Regression Equation Specification Error (RESET)
# Run RESET test (joint F-test on squared predicted values)
predicted_poly1 <- fitted(Model_poly1)
predicted_poly_squared1 <- predicted^2
Model_reset_poly1<- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + poly(GDP_per_Capita_1) + poly(Population_growth_1) + poly(Govt_edu_expenditure_1) + poly(Foreign_direct_investment_1) + I(predicted_poly_squared1), data = Energy_Data_1, index = c("country", "year"), model = "random")  # or "within" for fixed effects model)

predicted_poly2 <- fitted(Model_poly2)
predicted_poly_squared2 <- predicted^2
Model_reset_poly2 <- plm (Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + poly(GDP_per_Capita_2) + poly(Urban_Population_2) + poly(Research_Dev_expenditure_2) + poly(Foreign_direct_investment_2) +  I(predicted_poly_squared2), data = Energy_Data_2, , index = c("country", "year"), model = "random")  # or "within" for fixed effects model)

predicted_poly3 <- fitted(Model_poly3)
predicted_poly_squared3 <- predicted^2
Model_reset_poly3 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + poly(GDP_per_Capita_3) + poly(Population_growth_3) + poly(Govt_edu_expenditure_3)+ I(predicted_squared3), data = Energy_Data_3,  index = c("country", "year"), model = "random")  # or "within" for fixed effects model)

predicted_poly4 <- fitted(Model_poly4)
predicted_poly_squared4 <- predicted^2
Model_reset_poly4 <- plm (Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + poly(GDP_per_Capita_4) + poly(Urban_Population_4) + poly(Research_Dev_expenditure_4) + I(predicted_poly_squared4), data = Energy_Data_4, index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)

predicted_poly5 <- fitted(Model_poly5)
predicted_poly_squared5 <- predicted^2
Model_reset_poly5 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + poly(GDP_per_Capita_5) + poly(Population_growth_5) + poly(Foreign_direct_investment_5)+ I(predicted_poly_squared5), data = Energy_Data_5,  index = c("country", "year"), model = "random")  # or "within" for fixed effects model)

predicted_poly6 <- fitted(Model_poly6)
predicted_poly_squared6 <- predicted^2
Model_reset_poly6 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + poly(GDP_per_Capita_6) + poly(Urban_Population_6) + poly(Foreign_direct_investment_6) + I(predicted_poly_squared6), data = Energy_Data_6, index = c("country", "year"),
                   model = "random")  # or "within" for fixed effects model)

predicted_poly7 <- fitted(Model_poly7)
predicted_poly_squared7 <- predicted^2
Model_reset_poly7 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + poly(GDP_per_Capita_7) + poly(Urban_growth_7) + poly(Govt_edu_expenditure_7) + poly(Foreign_direct_investment_7) + I(predicted_poly_squared7), data = Energy_Data_7, index = c("country", "year"), model = "random")  # or "within" for fixed effects model)

predicted_poly8 <- fitted(Model_poly8)
predicted_poly_squared8 <- predicted^2
Model_reset_poly8 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + poly(GDP_per_Capita_8) + poly(Population_growth_8) + poly(Research_Dev_expenditure_8) +  poly(Foreign_direct_investment_8) + I(predicted_poly_squared8), data = Energy_Data_8, index = c("country", "year"), model = "random")  # or "within" for fixed effects model)

predicted_poly9 <- fitted(Model_poly9)
predicted_poly_squared9 <- predicted^2
Model_reset_poly9 <- plm(Renewable_energy_comb ~ Coal_consump_comb + Natural_gas_comb + Oil_consump_comb + Nuclear_consump_comb + poly(GDP_per_Capita_9) + poly(Urban_Population_9) + poly(Research_Dev_expenditure_9) + poly(Foreign_direct_investment_9)+ I(predicted_poly_squared8), data = Energy_Data_9,  index = c("country", "year"),model = "random")  # or "within" for fixed effects model)

# Extract RESET test result
reset_test_poly_result1<- summary(Model_reset_poly1)$fstatistic
reset_test_poly_result2 <- summary(Model_reset_poly2)$fstatistic
reset_test_poly_result3<- summary(Model_reset_poly3)$fstatistic
reset_test_poly_result4<- summary(Model_reset_poly4)$fstatistic
reset_test_poly_result5<- summary(Model_reset_poly5)$fstatistic
reset_test_poly_result6<- summary(Model_reset_poly6)$fstatistic
reset_test_poly_result7<- summary(Model_reset_poly7)$fstatistic
reset_test_poly_result8<- summary(Model_reset_poly8)$fstatistic
reset_test_poly_result9<- summary(Model_reset_poly9)$fstatistic

# Print RESET test results
print(reset_test_poly_result1)
print(reset_test_poly_result2)
print(reset_test_poly_result3)
print(reset_test_poly_result4)
print(reset_test_poly_result5)
print(reset_test_poly_result6)
print(reset_test_poly_result7)
print(reset_test_poly_result8)
print(reset_test_poly_result9)
```

#Results
H0: There are omitted variables and the functional form is not adequate.                                   
H1: There are no omitted variables and the functional form is adequate.
From the result above, the p-value is 2.2e-16 which is less than the 0.05 significance, so we reject the H0 and can conclude that there are no omitted variables and the functional form is adequate to explain the relationship between the dependent variable  and the independent variables.



```{r}
#Using Q-Q-plots for the residuals of models  
residuals_Model <- residuals(Model)
qqnorm(residuals_Model)
qqline(residuals_Model)
```

#Results
The quantiles of residuals in this model are plotted against the normal distribution quantiles. It can be inferred that the scatter plot of the residuals is generally normal because it goes roughly along the 45-degree line notwithstanding that there are a few variations in the upper and lower quantiles.    


```{r}
#Using Q-Q-plots for the residuals of models  
residuals_Model <- residuals(Model)
qqnorm(residuals_Model)
qqline(residuals_Model)
```



```{r}
#Using Q-Q-plots for the residuals of models  
residuals_Model1 <- residuals(Model1)
qqnorm(residuals_Model1)
qqline(residuals_Model1)
```

```{r}
#Using Q-Q-plots for the residuals of models  
residuals_Model6 <- residuals(Model6)
qqnorm(residuals_Model6)
qqline(residuals_Model6)
```




```{r}
#Using Q-Q-plots for the residuals of models  
residuals_model_poly <- residuals(Model_poly)
qqnorm(residuals_model_poly)
qqline(residuals_model_poly)
```


```{r}
#Using Q-Q-plots for the residuals of models  
residuals_model_poly6 <- residuals(Model_poly6)
qqnorm(residuals_model_poly6)
qqline(residuals_model_poly6)
```


```{r}
#Scale-Location-plots 
library(ggplot2)
residuals_vs_fitted <- ggplot(data.frame(residuals = residuals(Model), fitted_values = fitted(Model)), aes(x = fitted_values, y = residuals)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  labs(x = "Fitted Values", y = "Residuals") +
  ggtitle("Residuals vs. Fitted Values Plot") +
  theme_minimal()
print(residuals_vs_fitted)
```



```{r}
#Scale-Location-plots
library(ggplot2)
residuals_vs_fitted1 <- ggplot(data.frame(residuals = residuals(Model1), fitted_values = fitted(Model1)), aes(x = fitted_values, y = residuals)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  labs(x = "Fitted Values", y = "Residuals") +
  ggtitle("Residuals vs. Fitted Values Plot") +
  theme_minimal()
print(residuals_vs_fitted1)
```



```{r}
#Scale-Location-plots
residuals_vs_fitted6 <- ggplot(data.frame(residuals = residuals(Model6), fitted_values = fitted(Model6)), aes(x = fitted_values, y = residuals)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  labs(x = "Fitted Values", y = "Residuals") +
  ggtitle("Residuals vs. Fitted Values Plot") +
  theme_minimal()
print(residuals_vs_fitted6)
```
 
#Results
The scale-location-plot shows a clear trend of a biased shape in the distribution of residuals indicating heteroscedasticity. 

```{r}
#Scale-Location-plots using polynomials 
residuals_vs_fitted_poly <- ggplot(data.frame(residuals = residuals(Model_poly), fitted_values = fitted(Model_poly)), aes(x = fitted_values, y = residuals)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  labs(x = "Fitted Values", y = "Residuals") +
  ggtitle("Residuals vs. Fitted Values Plot") +
  theme_minimal()
print(residuals_vs_fitted_poly)
```





```{r}
#Scale-Location-plots using polynomials 
residuals_vs_fitted_poly6 <- ggplot(data.frame(residuals = residuals(Model_poly6), fitted_values = fitted(Model_poly6)), aes(x = fitted_values, y = residuals)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  labs(x = "Fitted Values", y = "Residuals") +
  ggtitle("Residuals vs. Fitted Values Plot") +
  theme_minimal()
print(residuals_vs_fitted_poly6)
```


#Second formular to test for multi-collinearity
```{r}
# Extract the model matrix
X1 <- model.matrix(col_gdp)

# Calculate the correlation matrix of the independent variables
cor_matrix <- cor(X1)

# Calculate the inverse of the correlation matrix
inv_cor_matrix <- solve(cor_matrix)

# Calculate VIF for each independent variable
vif <- diag(inv_cor_matrix)

# Print VIF values
print(vif)
```

#Manual test for collinearity-Code gotten from the R script
```{r}
col1<- plm(coal_consumption ~ gas_consumption + oil_consumption + nuclear_consumption, data = FullData1 , index = c("country", "year"), model = "within")  # or "within" for fixed effects model)
summary(col1)
1/(1-0.7751)
```


```{r}
# Selecting Breusch-Godfrey test for different lags
for (i in 1:10) {
  bg_test <- bgtest(M18, order = i)
  cat("Lag order:", i, "p-value:", bg_test$p.value, "\n")
}
```

